### 2022-05-30 main/chapter_2ljets.tex
\approx to approximately

Since signal models in $\twoljets$ do generate hard, invisible particles,
by selecting for large $\met$ we select events in which either there were real
invisible particles or something was badly mismeasured.
The standard selection for $\twoljets$-electroweak is $\met > 100\,\eV[G]$.
This is a nice round number, and corresponds roughly to where the $\met$-less
background $\zjets$ tails off.
This $100\,\eV[G]$ also corresponds roughly to several standard deviations of
a typical $\met$ noise scale of $\approx 10\textrm{--}30\,\eV[G]$, which I observe
by inspecting $\met / \metsig$ in $\twoljets$-electroweak selections,
and where $\metsig$ is defined in the next section.

>>>>

Since signal models in $\twoljets$ do generate hard, invisible particles,
by selecting for large $\met$ we select events in which either there were real
invisible particles or something was badly mismeasured.
The standard selection for $\twoljets$-electroweak is $\met > 100\,\eV[G]$.
This is a nice round number, and corresponds roughly to where the $\met$-less
background $\zjets$ tails off.
This $100\,\eV[G]$ also corresponds roughly to several standard deviations of
a typical $\met$ noise scale of approximately $10\textrm{--}30\,\eV[G]$, which I observe
by inspecting $\met / \metsig$ in $\twoljets$-electroweak selections,
and where $\metsig$ is defined in the next section.
